Younger, Unmarried, Childless, and Less Happy Americans Use the Internet the Most\thanks{Code and data are available at: https://github.com/AnnieYan0807/GSS-data-analysis.git.}

### 2023-03-16 outputs/paper/paper.tex
update changes

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={My title},
  pdfauthor={Sakura Ariga; Aliyah Maxine Ramos; Annie Yan},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{My title\thanks{Code and data are available at:
https://github.com/AnnieYan0807/GSS-data-analysis.git.}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{My subtitle if needed}
\author{Sakura Ariga \and Aliyah Maxine Ramos \and Annie Yan}
\date{15 March 2023}

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, breakable, boxrule=0pt, sharp corners, borderline west={3pt}{0pt}{shadecolor}, frame hidden, enhanced]}{\end{tcolorbox}}\fi

\hypertarget{introduction}{%
\section{1 Introduction}\label{introduction}}

You can and should cross-reference sections and sub-sections. For
instance, Section~\ref{sec-data} and Section~\ref{sec-first-point}.

\hypertarget{sec-data}{%
\section{2 Data}\label{sec-data}}

\hypertarget{survey}{%
\subsection{2.1 Survey}\label{survey}}

Saku

\hypertarget{key-features}{%
\subsubsection{2.1.1 Key Features}\label{key-features}}

Saku

\hypertarget{methodology}{%
\subsubsection{2.1.2 Methodology}\label{methodology}}

Saku

\hypertarget{strengths-weaknesses}{%
\subsubsection{2.1.3 Strengths \&
Weaknesses}\label{strengths-weaknesses}}

Saku

\hypertarget{questionnaire}{%
\subsection{2.2 Questionnaire}\label{questionnaire}}

Saku

\hypertarget{overview-of-data}{%
\subsection{2.3 Overview of Data}\label{overview-of-data}}

\hypertarget{data-source}{%
\subsubsection{2.3.1 Data Source}\label{data-source}}

Max

\hypertarget{variables-of-interest}{%
\subsubsection{2.3.2 Variables of
Interest}\label{variables-of-interest}}

Max

\begin{table}

\caption{A subset of key features}
\centering
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedleft}X}
\hline
Age & Sex & Race & Highest Degree & Number of Children & Marital Status & Happiness Level & Weekly Internet Hours\\
\hline
Ages 40 - 49 & Male & White & Bachelor's & 3 & Married & Pretty happy & 15\\
Ages 60 - 69 & Male & White & High school & 0 & Never married & Pretty happy & 5\\
Ages 70 - 79 & Male & White & Bachelor's & 2 & Married & Very happy & NA\\
Ages 40 - 49 & Female & White & High school & 4 & Married & Pretty happy & 7\\
Ages 50 - 59 & Female & White & Graduate & 2 & Married & Very happy & NA\\
Ages 50 - 59 & Female & White & Associate/junior college & 2 & Married & Very happy & 2\\
Ages 50 - 59 & Male & White & High school & 2 & Married & Pretty happy & 5\\
Ages 21 - 29 & Female & Other & High school & 3 & Married & Very happy & NA\\
\hline
\end{tabu}
\end{table}

Table :)

@@

\subcaption{\label{fig-agesidebyside-1}Subcaption}
\end{minipage}%
%
\begin{minipage}[t]{0.50\linewidth}

@@

\subcaption{\label{fig-agesidebyside-2}Subcaption}
\end{minipage}%

\caption{\label{fig-agesidebyside}Caption}

@@

Figure~\ref{fig-agesidebyside}

@@

\caption{\label{fig-childsandmarital}Caption}

@@

Figure~\ref{fig-childsandmarital}

@@

\caption{\label{fig-happiness}Caption}

@@

Figure~\ref{fig-happiness}

\hypertarget{results}{%
\section{3 Results}\label{results}}

@@

Figure~\ref{fig-ageandinternet} depicting the relationship between age
and average weekly internet usage. The data on internet usage hours for
various age groups are averaged to reduce any bias due to selectively
chosen survey responses. The curve on the graph is skewed to the right,
with its peak occurring in the 21 to 29 age group, which has the highest
internet usage of approximately 18 hours per week. Subsequently,
internet usage gradually declines with age, with the lowest usage
recorded in the 89+ age group at an average of 2 hours per week. This
graph indicates that young adults, particularly those aged 21 to 29,
spend more time on the internet. As people age, their internet usage
tends to decline gradually. The graph suggests a statistically
significant correlation between age and internet usage, and the trend is
relatively clear.

@@

Figure~\ref{fig-genderandinternet} illustrates the average weekly
internet usage of two genders. Similarly to the age and internet usage
graph, the data on internet usage hours for different genders are
averaged to minimize any volunteering bias. The data shows that there is
no substantial difference between male and female internet usage. Female
participants have an average of 12.9 hours per week spent on the
internet, while male participants have an slightly higher average of
13.3 hours per week spent on the internet. However, the gender selection
in this survey is limited, and further discussion regarding this
limitation can be found in the ethics and bias section
Section~\ref{sec-bias}.

@@

Figure~\ref{fig-raceandinternet} displays the average weekly internet
usage of individuals belonging to different races. Based on the data, we
can observe that individuals who do not identify as either Black or
White have the highest internet usage, with an average of 15.5 hours per
week. African American individuals have a similar level of internet
usage, also averaging 15.2 hours per week. In contrast, white
individuals tend to have the lowest internet usage, with an average of
12.3 hours per week.

{\centering \includegraphics{paper_files/figure-pdf/fig-personalincomeandinternet-1.pdf}

\caption{\label{fig-personalincomeandinternet}Average Weekly Total of
Internet Use by Personal Income}

Max - might emit\ldots{}

{\centering \includegraphics{paper_files/figure-pdf/fig-familyincomeandinternet-1.pdf}

\caption{\label{fig-familyincomeandinternet-1}Average Weekly Total of
Internet Use by Family Income}

{\centering \includegraphics{paper_files/figure-pdf/fig-familyincomeandinternet-2.pdf}

\caption{\label{fig-familyincomeandinternet-2}Average Weekly Total of
Internet Use by Family Income}

Max - might emit

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
]{article}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin = 1in]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Younger, Unmarried, Childless, and Less Happy Americans Use the Internet the Most},
  pdfauthor={Sakura Ariga; Aliyah Maxine Ramos; Annie Yan},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Younger, Unmarried, Childless, and Less Happy Americans Use the
Internet the Most\thanks{Code and data are available at:
https://github.com/AnnieYan0807/GSS-data-analysis.git.}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{An Analysis of the 2016 US General Social Survey}
\author{Sakura Ariga \and Aliyah Maxine Ramos \and Annie Yan}
\date{15 March 2023}

\begin{document}
\maketitle
\begin{abstract}
In this study, we investigated the 2016 United States General Social
Survey to gain an understanding of the characteristics of the people
that use the Internet the most, such as age, marital status, number of
children, and level of happiness. We did this by comparing the average
number of weekly Internet use across population groups. We found that
young adults that have never been married or have children and who are
not satisfied with their general happiness are those that use the
Internet the most. In an era in which the Internet is becoming more and
more used in the US, it is important to understand which population
group uses the Internet the most in order to inform public policies
surrounding Internet addiction and mental health.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, breakable, interior hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, frame hidden, boxrule=0pt]}{\end{tcolorbox}}\fi

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

The Internet has become a widely used computer network that allows for
connection, communication, and access to information. By the mid 1990s,
the Internet began reaching millions of users from around the world,
where using a web of information, known as the World Wide Web, was a
popular way of browsing information and facilitating communication
online ({``A Short History of the Internet''} 2020). Throughout the
years, the different ways in which the Internet is used have expanded,
and now users can also make purchases through electronic commerce
platforms and share different forms of media on social media platforms.

This report aims to investigate the characteristics of American adults
that use the Internet the most in comparison to those that use it the
least. We aim to understand the reasons why these factors are correlated
with a higher Internet use pattern and a lower Internet use pattern. Our
estimand is the mean number of weekly hours of Internet usage of
American adults. Using the survey data from the United States General
Social Survey (GSS) recorded in 2016, we constructed different models on
6 factors and their relationship with total weekly hours of Internet
use: age, race, sex, marital status, number of children, and happiness.

Through examining the relationships between the variables and the weekly
number of hours of Internet use, we found that young adults tend to use
the Internet more than older adults. This may be due to physical,
psychological, and social barriers when using the Internet. We also
found that those who have never been married use the Internet more than
others with different marital statuses. This could be related to age and
the difference in reasons for using the Internet. Additionally, as
social media is a large part of Internet usage, we found that the using
these platforms have a negative impact on emotional health,
demonstrating a possible correlation between high Internet usage and a
low level of happiness. These findings are important because using the
Internet more regularly can improve the lives of individuals for its
convenience and its accessibility. It is beneficial because it allows
for easier and instantaneous communication, for learning, for increasing
access to services, for encouraging connections and decreasing
isolation, and for gathering information (Lane 2022). However, the
consequences of increased Internet usage, such as Internet addiction and
mental health issues, should also be kept in mind. Our research on which
population groups use the Internet the most in the US can lay the
foundation for subsequent research investigating the pros and cons of
Internet use on different population groups, and the ways in which the
pros and cons affect those who use the Internet more.

The remainder of this report is structured as follows: Section 2
discusses the dataset of interest, including the methodology of the
survey and its strengths and weaknesses, Section 3 presents the results
through data visualizations, Section 4 discusses our findings, its
weaknesses, and next steps, and Section 5 consists of the supplementary
survey as an extension of the survey data to improve and enhance the
study.

\hypertarget{sec-data}{%
\section{Data}\label{sec-data}}

\hypertarget{survey}{%
\subsection{Survey}\label{survey}}

\hypertarget{key-features}{%
\subsubsection{Key Features}\label{key-features}}

The General Social Survey (GSS) is a national survey conducted in the
United States of America that aims to better understand trends in the
American adult population's social characteristics and attitudes to
better inform research and public policy ({``About the GSS,''} n.d.).
Beginning in 1972, this interview-based survey is conducted biennially
on five key themes: gender and marriage, current affairs, civil
liberties, politics, and religion and spirituality ({``Key Trends,''}
n.d.). The 2016 GSS is unique in that it also includes questions about
Internet-usage behaviours, which is why our analysis focuses on the GSS
of this year. In 2016, there is data for 2,867 respondents for 961
variables.

\hypertarget{methodology}{%
\subsubsection{Methodology}\label{methodology}}

The GSS' target population is adults aged 18 years and older living in
the United States. The sampling frame for the 2016 GSS is people living
in the US aged 18+ who can speak English or Spanish and live in
households ({``Frequently Asked Questions,''} n.d.). Thus, those living
outside households (e.g.~in university dorms, nursing homes,
institutions, military quarters) are not included in the GSS ({``GSS
1972-2018 Cross-Section Codebook: Appendix a - Sampling Design and
Weighting,''} n.d.). The frame was created using the NORC National
Sampling Frame, which first uses US Census data to stratify US
geographic regions by size and then chooses metropolitan areas and
non-metropolitan counties within these regions, as the first stage of
selection ({``GSS 1972-2018 Cross-Section Codebook: Appendix a -
Sampling Design and Weighting,''} n.d.). In the second stage of
selection, these metropolitan areas and non-metropolitan counties were
stratified by race and income and further divided into blocks ({``GSS
1972-2018 Cross-Section Codebook: Appendix a - Sampling Design and
Weighting,''} n.d.). Then, the sample is gathered by interviewers
beginning from the northwest corner of a given block and moving from
household to household until the equal-sex quota has been filled ({``GSS
1972-2018 Cross-Section Codebook: Appendix a - Sampling Design and
Weighting,''} n.d.).

Thus, the sample for the 2016 GSS was an area-probability sample
gathered by the clustered sampling approach, as households are selected
and then one random member from the household is selected to be included
in the survey ({``GSS 1972-2018 Cross-Section Codebook: Appendix a -
Sampling Design and Weighting,''} n.d.). A key tradeoff of this approach
is that, while this method is much easier than solely random sampling,
it can lead to bias in that there is more bias if the clusters are
similar to each other.

Non-response is handled by inputting it in the GSS dataset as one of the
following options depending on the method of non-response: ``NA'', ``no
answer'', ``do not know'', or ``skipped''.

\hypertarget{strengths-weaknesses}{%
\subsubsection{Strengths \& Weaknesses}\label{strengths-weaknesses}}

A strength of this 2016 GSS survey was that it was delivered both in
English and in Spanish, allowing for a greater reach than had the survey
just been conducted in English, like in the years previous to 2006
({``GSS 1972-2018 Cross-Section Codebook: Appendix a - Sampling Design
and Weighting,''} n.d.). Of the people who had been excluded from this
survey due to the English-only delivery, Spanish-speakers made up the
majority, so this dual language delivery addressed this key exclusion
({``GSS 1972-2018 Cross-Section Codebook: Appendix a - Sampling Design
and Weighting,''} n.d.).

A weakness of this sample is the lack of a gender variable, as the
sample only provides a variable on sex. A gender variable would be more
useful for data analysis, as it better reflects the respondent's lived
experience. The lack of a gender variable that better accommodates for
people's lived experience might lead to those who feel uncomfortable
with the binary categories of sex to refrain from participating in the
survey, leading to selection bias.

Another weakness of the 2016 GSS survey is that the interviewer
physically fills out the responses for the respondent. This can
potentially lead to measurement error. When the interviewer fills out
the survey on behalf of the respondent, there may be a difference in the
observed responses of the interviewer and the actual responses of the
interviewee. This creates difficulty in verifying responses ({``For
Survey Participants,''} n.d.).

A third weakness of the survey is the role of selection bias that exists
due to the inability to reach the entire population. The survey may also
be susceptible to volunteering bias because the data is reliant on
participants willingly providing their answers, which could lead to
biased results.

\hypertarget{sec-questionnaire}{%
\subsection{Questionnaire}\label{sec-questionnaire}}

A strength of the questionnaire was the clear wording of the question
regarding Internet usage per week in hours. The survey question was
formatted as follows: ``Not counting e-mail, about how many minutes or
hours per week do you use the Web? (Include time you spend visiting
regular web sites and time spent using interactive Internet services
like chat rooms, Usenet groups, discussion forums, bulletin boards, and
the like.)'' ({``GSS Data Explorer: NORC at the University of Chicago''}
(n.d.)). The providing of examples was likely helpful in stimulating the
respondents' memory of what exactly Internet usage can look like, as if
one is flat out asked whether they use the Internet, it can be hard to
conceptualize what that looks like.

A key weakness of this questionnaire is the race variable, as it only
allows for three options: ``Black'', ``White'', or ``Other'', which does
not take into account the largest ethnic minority group, Hispanics and
Latino Americans, as well as other ethnic groups, such as Asians and
Indigenous Americans in the United States. In comparison, while not
without fault itself, the US Census identifies 5 minimum categories of
race (White, Black or African American, American Indian or Alaska
Native, Asian, Native Hawaiian or Other Pacific Islander) and also
allows for the reporting of more than one race (Bureau 2022). The
questionnaire should at least have followed these US Census minimum race
categories.

Another weakness of this questionnaire is that questions are allowed
non-responses. This results in truncated data, in which the dataset has
been incompletely collected. Having no response for a question can only
be observed as null, despite there being a possible actual value
(Alexander 2023). There are a variety of reasons as to why a respondent
may not want to answer a question, but can only be observed as a
non-response by researchers to avoid biased assumptions and inaccurate
results.

\hypertarget{overview-of-data}{%
\subsection{Overview of Data}\label{overview-of-data}}

\hypertarget{data-source}{%
\subsubsection{Data Source}\label{data-source}}

In this report, the 2867 observations from the 2016 United States
General Social Survey are used. The survey data was obtained from the
University of Chicago National Opinion Research Centre (NORC) ({``GSS
Data Explorer: NORC at the University of Chicago,''} n.d.).

This report was created using the R statistical programming language (R
Core Team 2020). The here package was utilized to retrieve files from
another folder within the same R project (Müller 2020). For the results
and analysis of this report, all figures were created using the
tidyverse package (Wickham et al. 2019). Additionally, the tables were
created using the packages knitr (Xie 2023) and kableExtra (Zhu 2021),
and the graphs were created using the packages lessR (Gerbing 2021),
tidyr (Wickham, Vaughan, and Girlich 2023), and ggplot2 (Wickham 2016).

\hypertarget{variables-of-interest}{%
\subsubsection{Variables of Interest}\label{variables-of-interest}}

Our report selects 7 variables for analysis. We focus on 6 particular
factors that we predicted affects the amount of Internet use: age, sex,
race, number of children, marital status, and happiness. In this paper,
we investigate the influence of these various factors on the total
number of hours of weekly Internet usage. The packages tidyverse
(Wickham et al. 2019), haven (Wickham, Miller, and Smith 2022), and
reshape2 (Wickham 2007) were used to clean the dataset by grouping or
converting the questionnaire responses into categorical or textual
answers.

\hypertarget{tbl-variables}{}
\begin{table}

\caption{\label{tbl-variables}The Variables of Interest }The Variables of Study}
\centering
\begin{tabu} to \linewidth {>{\raggedleft}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\hline
Weekly Internet Hours & Age & Sex & Race & Number of Children & Marital Status & Happiness Level\\
\hline
15 & Ages 40 - 49 & Male & White & 3 & Married & Pretty happy\\
5 & Ages 60 - 69 & Male & White & 0 & Never married & Pretty happy\\
NA & Ages 70 - 79 & Male & White & 2 & Married & Very happy\\
7 & Ages 40 - 49 & Female & White & 4 & Married & Pretty happy\\
NA & Ages 50 - 59 & Female & White & 2 & Married & Very happy\\
2 & Ages 50 - 59 & Female & White & 2 & Married & Very happy\\
5 & Ages 50 - 59 & Male & White & 2 & Married & Pretty happy\\
\hline
\end{tabu}
\end{table}

Table~\ref{tbl-variables} shows the first 10 rows of the cleaned
dataset. The variables, Number of Children and Weekly Internet Hours,
are recorded as a numerical value. Weekly Internet Hours has a maximum
value of 168, as there are only 168 hours in a week. Age is also
recorded as a numerical value, but is cleaned to represent ages in
groups of ten years. The other variables, Sex, Race, Marital Status, and
Happiness Level, are all recorded as a textual option for respondents to
choose from.

@@

\subcaption{\label{fig-agesidebyside-1}Relationship between Age and Sex}
\end{minipage}%
%
\begin{minipage}[t]{0.50\linewidth}

@@

\subcaption{\label{fig-agesidebyside-2}Relationship Between Age and
Race}
\end{minipage}%

\caption{\label{fig-agesidebyside}Relationship between Age and Sex and
Age and Race}

@@

Most of the respondents of the 2016 GSS are adults ranging from ages 21
to 69 years old. The size of each age group between that range
oscillates within the right skewed distribution. The largest age group
respondent size is 50 to 59 years old. By graphing the variables, age
and sex in Figure~\ref{fig-agesidebyside}, we observe that there are
more female adults in each age group participating in this survey than
there are male adults. The overall distribution is skewed to the right.
The visualization of age and race in Figure~\ref{fig-agesidebyside}
demonstrates that the respondents that identify with the White racial
group comprises most of the respondent sample. This racial group is also
shown to have a near-symmetrical distribution. Conversely, the other
racial groups in this survey, Black and Other, are significantly the
minority of the survey sample. The Black and Other racial groups are
skewed to the right, illustrating that there are less individuals that
identify with these racial groups in the older age groups. According to
the 2020 US Census surveys, the most common racial group in America is
White or Caucasian, which means that the 2016 GSS data on this group
provides a relatively accurate representation of American society
(Jensen 2022).

@@

\caption{\label{fig-childsandmarital}Relationship between Marital Status
and Number of Children}

@@

According to Figure~\ref{fig-childsandmarital}, respondents who are
married have a right skew distribution of the number of children they
have, where the mode of the data is having two children. As for
individuals that responded as never having been married, the
distribution was exponential, in which the mode of this distribution is
having zero children. As the number of children increases, the number of
individuals who have never been married decreases. The distribution of
the other minority marital groups are skewed to the right. Overall, most
survey respondents have zero children.

@@

\caption{\label{fig-happiness}Happiness Level Responses from Survey
Respondents}

@@

Figure~\ref{fig-happiness} demonstrates general happiness trends and
exhibits a left skew distribution. This illustrates that a significant
proportion of the respondents indicate that they are fairly happy and an
adequate proportion indicate that they are very happy. With a limited
number of options to measure happiness quantitatively, it is difficult
to discern a distribution on varying levels of happiness.

\hypertarget{results}{%
\section{Results}\label{results}}

@@

Figure~\ref{fig-ageandinternet} depicts the relationship between age and
average weekly Internet usage. The data on Internet usage hours for
various age groups are averaged to reduce any bias due to selectively
chosen survey responses. The curve on the graph is skewed to the right,
with its peak occurring in the 21 to 29 age group, which has the highest
Internet usage of approximately 18 hours per week. Subsequently,
Internet usage gradually declines with age, with the lowest usage
recorded in the 89+ age group at an average of 2 hours per week. This
graph indicates that young adults, particularly those aged 21 to 29,
spend more time on the Internet. As people age, their Internet usage
tends to decline gradually. The graph suggests a statistically
significant correlation between age and Internet usage, and the trend is
relatively clear.

@@

Figure~\ref{fig-genderandinternet} illustrates the average weekly
Internet usage of two sexes. Similar to the age and Internet usage
graph, the data on Internet usage hours for different genders are
averaged to minimize any volunteering bias. The data shows that there is
no substantial difference between male and female Internet usage. Female
participants have an average of 12.9 hours per week spent on the
Internet, while male participants have a slightly higher average of 13.3
hours per week spent on the Internet. However, the gender selection in
this survey is limited, and further discussion regarding this limitation
can be found in the ethics and bias section Section~\ref{sec-bias}.

@@

Figure~\ref{fig-raceandinternet} displays the average weekly Internet
usage of individuals belonging to different races. Based on the data, we
can observe that individuals who do not identify as either Black or
White have the highest Internet usage, with an average of 15.5 hours per
week. Black individuals have a similar level of Internet usage, also
averaging 15.2 hours per week. In contrast, White individuals tend to
have the lowest Internet usage, with an average of 12.3 hours per week.
